### 2018-07-12 FrascatiPlot/Paper/NucleiB2.tex
We are very grateful

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%              APPENDIX                   %%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{appendix}
\section{Relation to the Sato-Yazaki coalescence model}\label{appendix:Sato}
%As discussed in~\cite{Nagle:1996vp}, 
The approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium in contrast to~\cite{Scheibl:1998tk}. It assumes no correlation between different nucleons and no correlation between coordinates in space and momentum. In a heavy ion collisions, such correlations are consequence of hydrodynamical flow. 
The coalescence process to form a nucleus with mass number $A = Z + N$ is formulated in terms of the momentum per nucleon ($p$) as
%
\begin{equation}
\frac{\gamma_{A}}{\sigma_{A,0}} \frac{d^{3}\sigma_{A}}{d^{3}p} =  \left( {4 \over 3} \pi p_{0}^{3}\right)^{A-1}\frac{1}{Z! N!} \left(\frac{\gamma_{p}}{\sigma_{p,0}} \frac{d^{3}\sigma_{p}}{d^{3}p_{p}}\right)^{Z} \left(\frac{\gamma_{n}}{\sigma_{n,0}} \frac{d^{3}\sigma_{n}}{d^{3}p_{n}}\right)^{N} 
\end{equation} 
%
where $p_{0}$ corresponds to the coalescence momentum, $\gamma_{A}$ and $\gamma_{p,n}$ are the Lorentz factors for the nucleus and the nucleons, respectively. The reaction cross sections are denoted as $\sigma_{i,0}$, where $A = p, n, A$.
Assuming that the proton and neutron emission probabilities are equal and that $p_{p} \approx p_{n} \equiv p$, this expression relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as

@@

%%%%% acknowledgements
\newenvironment{acknowledgement}{\relax}{\relax}
\begin{acknowledgement}
\section*{Acknowledgements}
We thank U. Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii.
The authors would like to thank themselves for the auto-critics.

>>>>

%%%%% acknowledgements
\newenvironment{acknowledgement}{\relax}{\relax}
\begin{acknowledgement}
\section*{Acknowledgements}
We thank U. Heinz for the useful discussions and the clarification on the equivalence of the Bertsch-Pratt and Yano-Koonin-Podgoretskii parameterisations of the HBT radii. We further acknowledge discussions with Benjamin Doenigus about the production of \hthreelambda\ in pp collisions. In addition, we would like to thank Juergen Schukraft, Peter Braun-Munzinger, Roman Lietava, Kfir Blum and the colleagues from the ALICE Collaboration for their valuable input.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%              APPENDIX                   %%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendix}
\section{Relation to the Sato-Yazaki coalescence model}\label{appendix:Sato}
%As discussed in~\cite{Nagle:1996vp}, 
The approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium in contrast to~\cite{Scheibl:1998tk}. It assumes no correlation between different nucleons and no correlation between coordinates in space and momentum. In a heavy ion collisions, such correlations are consequence of hydrodynamical flow. 
The coalescence process to form a nucleus with mass number $A = Z + N$ is formulated in terms of the momentum per nucleon ($p$) as
%
\begin{equation}
\frac{\gamma_{A}}{\sigma_{A,0}} \frac{d^{3}\sigma_{A}}{d^{3}p} =  \left( {4 \over 3} \pi p_{0}^{3}\right)^{A-1}\frac{1}{Z! N!} \left(\frac{\gamma_{p}}{\sigma_{p,0}} \frac{d^{3}\sigma_{p}}{d^{3}p_{p}}\right)^{Z} \left(\frac{\gamma_{n}}{\sigma_{n,0}} \frac{d^{3}\sigma_{n}}{d^{3}p_{n}}\right)^{N} 
\end{equation} 
%
where $p_{0}$ corresponds to the coalescence momentum, $\gamma_{A}$ and $\gamma_{p,n}$ are the Lorentz factors for the nucleus and the nucleons, respectively. The reaction cross sections are denoted as $\sigma_{i,0}$, where $A = p, n, A$.
Assuming that the proton and neutron emission probabilities are equal and that $p_{p} \approx p_{n} \equiv p$, this expression relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as

@@
